```{r}
library(leaflet)
library(ggplot2)
library(tidyverse)
#install.packages("gganimate")
library(gganimate)
library(lubridate)
```


```{r load-data, echo = FALSE}

nyc_squirrels <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-29/nyc_squirrels.csv")
```

```{r cleaning-data}
nyc_squirrels <- nyc_squirrels %>%
  mutate(day_of_week = case_when(
    date %in% c(10062018, 10072018, 10132018, 10142018, 10202018, 10212018, 10272018, 10282018) ~ "weekend",
    TRUE ~ "weekday"
  ))
```

```{r behavior-variable-merge}
nyc_squirrels <- nyc_squirrels %>%
  mutate(behavior = case_when(
    running == TRUE ~ "running",
    chasing == TRUE ~ "chasing",
    climbing == TRUE ~ "climbing",
    eating == TRUE ~ "eating",
    foraging == TRUE ~ "eating",
    TRUE ~ "other"
  ))
```

```{r noise-variable-merge}
nyc_squirrels <- nyc_squirrels %>%
  mutate(noise = case_when(
    kuks == TRUE ~ "kuks",
    quaas == TRUE ~ "quaas",
    moans == TRUE ~ "moans",
    TRUE ~ "no noise"
  ))
```

```{r behavior-density-faceted-by-weekend}
ggplot(nyc_squirrels, aes(x = behavior, color = behavior, fill = behavior)) +
  geom_histogram(stat = "count") +
  facet_wrap(~day_of_week) + 
  scale_fill_viridis_d()
```

```{r stacked_bar}
ggplot(nyc_squirrels, aes(fill = primary_fur_color, x = behavior, y = primary_fur_color)) + 
    geom_bar(position = "stack", stat = "identity") +
    scale_fill_manual(values = c("Black", "bisque3", "dimgray"), na.value = "lightskyblue1")
  
```


```{r noise-faceted-by-weekend}
ggplot(nyc_squirrels, aes(x = noise, color = noise, fill = noise)) +
  geom_histogram(stat = "count") +
  facet_wrap(~day_of_week) +
  scale_fill_viridis_d()
```

```{r noise-faceted-by-weekend-remove-no-noise}
## Can i remove the "no noise" observation? 
ggplot(nyc_squirrels, aes(x = noise, color = noise, fill = noise)) +
  geom_histogram(stat = "count") +
  facet_wrap(~day_of_week) + 
  scale_fill_viridis_d()
```

```{r}
nyc_squirrels %>%
  ggplot(na.rm = TRUE, aes(x = long, y = lat, color = primary_fur_color)) +
  labs(title = "Position of Squirrel by Fur Color") +
   scale_color_manual(values = c("Black", "bisque3", "dimgray"), na.value = "lightskyblue1") +
  geom_point()
```


```{r leaflet-map-color}
pal_coats <- colorFactor(c("Black", "bisque3", "dimgray", "lightskyblue1"), domain = c("Black", "Cinnamon", "Grey", "NA"))

#Locations based on fur color
nyc_squirrels %>%
  filter(!is.na(primary_fur_color)) %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(lng = ~long,
                   lat = ~lat, radius = 3, color = ~pal_coats(primary_fur_color), stroke = FALSE, fillOpacity = 0.5) %>%
  addLegend(position ="bottomright",pal = pal_coats, values = ~primary_fur_color)
```

```{r leaflet_behavior}

pal_behavior <- colorFactor(c("steelblue", "springgreen", "slateblue", "violet", "tomato"), domain = c("chasing", "climbing", "eating", "running", "other"))

#Locations based on behavior
nyc_squirrels %>%
  filter(!is.na(behavior)) %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(lng = ~long,
                   lat = ~lat, radius = 3, color = ~pal_behavior(behavior), stroke = FALSE, fillOpacity = 0.5) %>%
  addLegend(position ="bottomright",pal = pal_behavior, values = ~behavior)
```


```{r pie-chart-fur-color}
ggplot(data = nyc_squirrels, aes(x = "", y = primary_fur_color, fill = primary_fur_color)) +
  geom_col() + 
  labs(title = "Distribution of Primary Fur Color Among Squirrels in NYC", x = "", y = "") +
  coord_polar(theta = "y") + 
  scale_fill_brewer() + 
   scale_fill_manual(values = c("Black", "bisque3", "dimgray"), na.value = "lightskyblue1") +
  theme_void()
```

```{r}
library(stringr)
nyc_squirrels$hectare_number <- str_sub(nyc_squirrels$hectare,1,2) 
nyc_squirrels$hectare_letter <- str_sub(nyc_squirrels$hectare,3,3) 
```


```{r}

nyc_squirrels <- nyc_squirrels %>%
  mutate(date = mdy(date),
         hectare_number = as.numeric(hectare_number),
         day = day(date))

```


```{r}

# Library
library(ggspatial)
 
# For google map, you have to give the center of the window you are looking at.
# Possibility for the map type argument: terrain / satellite / roadmap / hybrid
 
map1 <- ggplot(nyc_squirrels, aes(x = long, y = lat, color = behavior)) +
  annotation_map_tile(type = "thunderforestoutdoors") +
  geom_spatial_point()

map_anim <- map1 +
  transition_time(day)  +
  labs(title = "Day: {frame_time}") 

animate(map_anim, renderer = ffmpeg_renderer())

anim_save("map_anim.gif")

```



```{r}

nyc_squirrels_sum <- nyc_squirrels %>%
  group_by(day, hectare_letter, hectare_number) %>%
  summarise(squirrel_activity = sum(hectare_squirrel_number, na.rm = TRUE))

p2 <- ggplot(nyc_squirrels_sum, aes(hectare_number, hectare_letter, fill= squirrel_activity)) + 
  geom_tile() + 
  facet_wrap(~day)
  

p2

p1 <- ggplot(nyc_squirrels_sum, aes(as.numeric(hectare_number), hectare_letter, fill= squirrel_activity)) + 
  geom_tile() 

p3 <- p1 + 
  transition_time(day) +
  labs(title = "Day: {frame_time}") +
  shadow_mark()

animate(p3, renderer = ffmpeg_renderer())

anim_save("heatmap3.gif")

```
# scale label manual
# use scale to add manual axis labels
=======

```


```{r Age Distribution of Squirrels }

squirrel_ages <- nyc_squirrels %>%
  mutate(age = na_if(age,'?'), n=1) %>%
  group_by(age) %>%
  summarize(age_sum = sum(n)) %>%
  ungroup() %>%
  mutate(total = sum(age_sum), dummy = '') %>%
  summarize(age, age_sum, total, dummy, pct_age = (age_sum/total)*100)

squirrel_ages[is.na(squirrel_ages)] <- "Unknown"


ggplot(squirrel_ages, aes(x=dummy, y= pct_age, fill=age)) +
  geom_col() +
  geom_text(aes(label=paste0(round(pct_age,digits=2), "%")), 
            position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Paired") +
    theme_minimal(base_size = 16) +
    labs(x = "Total Population", 
         y ="Percentage", 
         fill='Age Group') +
   ggtitle('Central Park Squirrel Population by Age Group') +
    theme(plot.title = element_text(hjust = 0.5)) 
    
```


```{r Color of Squirrels Based on Age }

 nyc_squirrels %>%
  filter(age !='?') %>%
  mutate(n=1)%>%
  group_by(age) %>%
  ggplot() +
    geom_col(aes(y=n,x=age, fill=primary_fur_color), position="fill") +
    ggtitle('Demographics of Central Park Squirrels') +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs( x='Age Group', y= 'Proportion') +
    labs(fill='Primary Fur Color') +
    scale_fill_manual(values = c("black", "bisque3", "dimgray", "lightskyblue1"))
```

